\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-02-06 manuscript.Rmd
Method: Item Generation $ Item Selection Formalized

  An expert panel prepared the initial 48 item pool. Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones). Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime). In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09). The internal consistency reliability coefficient for the total instrument was McDonald’s omega_total=0.73. Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05). Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).

@@

## Item Generation

To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales. However, no scales specifically measuring the behavioural component of light exposure were found (see Table \@ref(tab:reltab2)). Consequentially we pursued to introduce a new openly available scale to address this research gap. For this purpose, an expert researcher panel from the fields of chronobiology, light research, neuroscience, and psychology – comprising all authors of the present manuscript – generated and collected preliminary item ideas. Special attention was paid to design items circumscribed to assess light exposure *behaviour* as opposed to subjective measurements of the light environment [@eklund1996development; @dianat2013objective]) and semi-quantitative assessments of light sources' illuminance [@bajaj2011validation] in order to maintain content validity. In a collective effort the generated items were then peer-reviewed, amended, unified, and complemented with a suitable response scale (5-point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always"). This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.

## Survey characteristics

@@

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line(colour ='#DC000099')+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1.5,colour ='#3C5488FF')+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
#text = element_text(size = 25

@@

fator2 <- cowplot::plot_grid(parallel, scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=3, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors2.png",fator2, width = 18, height = 6, dpi = 600)
```

@@

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015]. We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers**(n= `r mi.count[1,2]`) and **non-native English speakers** (n = `r mi.count[2,2]`). For a detailed description these two groups please see Sup. Table \@ref(tab:midesp). Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring]. Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. 
The invariance model fit of our tool was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999]. We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272]. Table \@ref(tab:InvarianceTab) summarized the fit indices. The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attained the highest level of the MI. A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.

>>>>

  An expert panel prepared the initial 48 item pool spanning different light exposure related behaviors. Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey yielding responses from an international sample (690 completed responses, 74 countries, 28 time zones). Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime). In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09). The internal consistency reliability coefficient for the total instrument was McDonald’s omega_total=0.73. Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05). Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).

@@

## Data Collection

@@

## Item Construction & Item Selection

After reviewing the literature, we identified several light exposure related scale. However, no scales specifically measuring the behavioural component of light exposure were found. As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale.The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel. The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology. The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any. The author team acknowledged the auggestions and amended the items as required thus creating a 48-item scale

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line(colour ='#DC000099')+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1.5,colour ='#3C5488FF')+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
#text = element_text(size = 25

@@

fator2 <- cowplot::plot_grid(scree.plot,Hull, 
                   labels = "AUTO",
                   ncol=3, 
                  align = "v", 
                  label_fontfamily = "Arial",
                  label_fontface = "plain")
ggsave("Manuscript.figures/factors2.png",fator2, width = 18, height = 6, dpi = 600)
```

@@

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015]. We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers**(n= `r mi.count[1,2]`) and **non-native English speakers** (n = `r mi.count[2,2]`). For a detailed description these two groups see Sup. Table \@ref(tab:midesp). Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring]. Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. 
The invariance model fit of our tool was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999]. We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272]. Table \@ref(tab:InvarianceTab) summarized the fit indices. The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attained the highest level of the MI. A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.
